---
title: "Using Cohort Pathways"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using Cohort Pathways}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
# Set global chunk options for RMarkdown rendering
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#### Load required libraries
```{r setup}

# Install 'tidyOhdsiRecipies' package if not already available
# remotes::install_github('OdyOSG/tidyOhdsiRecipies')

rlang::check_installed("tidyOhdsiRecipies")
rlang::check_installed("CohortGenerator")
# Load CohortPathways and connection functionality
library(CohortPathways)

# Generate connection details to a sample CDM (using the Eunomia demo database)
connectionDetails <- Eunomia::getEunomiaConnectionDetails()
```

### Step 1, 2: Define Cohort Definitions, Generate Cohorts
```{r}
# grabbed from https://github.com/darwin-eu-dev/TreatmentPatterns
generationSet <- tidyOhdsiRecipies::createCohortDefinitionSet(
  path = system.file(package = "CohortPathways", "exampleCohorts")
)

CohortGenerator::runCohortGeneration(
  connectionDetails = connectionDetails,
  cdmDatabaseSchema = 'main',
  cohortDatabaseSchema = 'main',
  cohortTableNames = CohortGenerator::getCohortTableNames('cp_cohorts'),
  cohortDefinitionSet = generationSet,
  outputFolder = 'tmpor_folder'
)

```


###Step 3: Execute Pathway Analysis
The executeCohortPathways function identifies the treatment pathways for a target cohort and a set of event cohorts. In this example, we analyze pathways for a target cohort (viral sinusitis) and events cohorts defined in the range 1:6.

```{r}

cpResults <- CohortPathways::executeCohortPathways(
  connectionDetails = connectionDetails,
  cohortDatabaseSchema = 'main',
  cohortTableName = 'cp_cohorts',
  targetCohortIds = c(7), # viral sinusitis
  eventCohortIds = c(1:6) # event cohorts
)
# Inspect the names of the results
names(cpResults)
```
### Step 4: Visualize Treatment Pathways with a Sunburst Plot

```{r}
# Create and display a sunburst plot for treatment pathways
createPathwaySunburst(
    cpResults,
    generationSet,
    nPaths = 3,
    minCount = 5)
```
```{r}
## move utlt folder 
unlink('tmpor_folder', recursive = TRUE)
```




